\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[scale=0.78]{geometry}

% Official company & director details
\name{Welcome Xolani}{Bungu}
\title{Founder \& Managing Director \\ 1875 NN PROMOTION AND EVENTS (PTY) LTD}
\address{10 Landa Avenue}{Sunnyridge, East London}{Eastern Cape 5142 \\ South Africa}
\mobile{+27 73 940 7800}
\email{aselumi1975@gmail.com}
\extrainfo{CIPC Registration: 2025/339607/07 \\ Private Company (Pty) Ltd – In Business since 24 April 2025}

\begin{document}

\makecvtitle

\vspace{-10pt}
\begin{center}
    \large\textbf{Company Business Profile} \\
    \vspace{4pt}
    \normalsize 1875 NN PROMOTION AND EVENTS (PTY) LTD \\
    \small Registered under CIPC Enterprise Number 2025/339607/07
\end{center}

\vspace{8pt}

\section{Company Overview}
\cvitem{}{1875 NN PROMOTION AND EVENTS (PTY) LTD is a registered private company specialising in professional event management, brand promotions, activations, and related services in the Eastern Cape and beyond.}
\cvitem{}{Led by Founder \& Managing Director Welcome Xolani Bungu, the company delivers safe, compliant, high-impact events with a strong commitment to community engagement, regulatory adherence, and client satisfaction.}

\section{Official Registration Details (CIPC Certificate)}
\cvitem{Enterprise Number}{2025/339607/07}
\cvitem{Full Enterprise Name}{1875 NN PROMOTION AND EVENTS (PTY) LTD}
\cvitem{Registration Date}{24 April 2025}
\cvitem{Enterprise Type}{Private Company (Pty) Ltd}
\cvitem{Status}{In Business}
\cvitem{MOI Type}{Standard (COR15.1A)}
\cvitem{Main Business Object}{Business activities not restricted}
\cvitem{Financial Year End}{February}
\cvitem{Registered Office \& Postal Address}{10 Landa Avenue, Sunnyridge, East London, Eastern Cape, 5142}
\cvitem{Director}{Welcome Xolani Bungu \\ (Active Director, Appointed 24 April 2025)}

\section{Core Services}
\cvlistdoubleitem{Event Management \& Coordination}{Complete planning and delivery of concerts, festivals, cultural celebrations, corporate functions and public gatherings.}
\cvlistdoubleitem{Brand Activations \& Experiential Marketing}{Innovative, high-visibility campaigns designed to engage target audiences.}
\cvlistdoubleitem{Promotions \& Sponsorship Management}{Strategic promotions, artist/talent booking, sponsor partnerships and ROI optimisation.}
\cvlistdoubleitem{Marketing \& Publicity}{Multi-channel campaigns (digital, radio, social media, outdoor).}
\cvlistdoubleitem{Bush Clearance \& Venue Preparation}{Site clearing, ground preparation and setup for outdoor and temporary venues.}
\cvlistdoubleitem{Staff Training \& Skills Development}{Event crew training in crowd management, safety protocols, customer service and emergency response.}
\cvlistdoubleitem{Risk \& Safety Compliance}{Full ESSPC safety planning, SAPS liaison, certificate procurement (venue grading, fire, public liability, structural, electrical).}
\cvlistdoubleitem{Logistics \& Technical Services}{Audio-visual, staging, lighting, sound, transport and infrastructure management.}

\section{Experience Highlights}
\cvlistitem{Proven track record delivering SAPS medium-risk categorised events at major venues including ABSA Stadium (B Field) and Buffalo Park Cricket Stadium, East London.}
\cvlistitem{Strong collaborative relationships with SAPS Eastern Cape Provincial Office, Buffalo City Metro, sponsors, media partners and local communities.}
\cvlistitem{Active focus on job creation, youth empowerment and skills transfer through event staffing and training initiatives.}

\section{Compliance Statement}
\cvitem{}{The company operates in full compliance with:}
\cvlistitem{Safety at Sports and Recreational Events Act 2 of 2010 (SASREA)}
\cvlistitem{Private Security Industry Regulation Act 56 of 2001 (PSIRA)}
\cvitem{}{All required certificates and insurance are routinely obtained and maintained for every event.}

\section{Contact Information}
\cvitem{Managing Director}{Welcome Xolani Bungu}
\cvitem{Mobile}{+27 73 940 7800}
\cvitem{Email}{aselumi1975@gmail.com}
\cvitem{Registered Address}{10 Landa Avenue, Sunnyridge, East London, Eastern Cape, 5142}
\cvitem{Company}{1875 NN PROMOTION AND EVENTS (PTY) LTD \\ CIPC 2025/339607/07}

\section{Mission Statement}
\cvitem{}{To organise and deliver extraordinary, safe, inclusive and professionally executed events that strengthen brands, unite communities, create economic opportunities and exceed stakeholder expectations.}

\end{document}